% 	HTML5 Robot User Interface Project Report: Bibliography
% 	An ASLab Project,
% 	Developed by Daniel Peiró
% 	ETSII, UPM 2014-2015
\addcontentsline{toc}{chapter}{References}
\renewcommand{\bibname}{References}
\begin{thebibliography}{99}

\bibitem{httpW3}
  The Internet Society,
  \emph{\href{http://tools.ietf.org/html/rfc2616}{Hypertext Transfer Protocol -- HTTP/1.1}},  
  1999.

\bibitem{bernerslee09}
  Tim Berners-Lee,
  \emph{\href{http://www.ted.com/talks/tim_berners_lee_on_the_next_web?language=en}{Tim Berners-Lee TED Talk on the Next Web}},  
  2009.

\bibitem{raggett98}
  Dave Raggett,
  \emph{\href{http://www.w3.org/People/Raggett/book4/ch02.html}{Raggett on HTML 4 (Chapter 2: A history of HTML)}},  
  1998.

\bibitem{marshall12}
  James Marshall,
  \emph{\href{http://www.jmarshall.com/easy/http/}{HTTP Made Really Easy}},  
  2012.
  
\bibitem{goldfarb96}
Charles F. Goldfarb,
\emph{\href{http://www.sgmlsource.com/history/roots.htm}{The Roots of SGML -- A Personal Recollection}},  
1996.

\bibitem{rauschmayer14}
Dr. Axel Rauschmayer,
\emph{\href{http://speakingjs.com/es5/}{Speaking JavaScript -- An In-Depth Guide for Programmers (Free Online Version)}},  
2014.

\bibitem{liebos99}
Håkon Wium Lie and Bert Bos,
\emph{\href{http://www.w3.org/Style/LieBos2e/history/Overview.html}{Cascading Style Sheets, designing for the Web}},  
1999.

\bibitem{w3c11}
World Wide Web Consortium,
\emph{\href{http://www.w3.org/html/logo/faq.html}{W3C HTML5 Logo FAQ}},  
2011.

\bibitem{w3cwebquality02}
W3C Quality Assurance Interest Group,
\emph{\href{http://www.w3.org/QA/2002/04/Web-Quality}{W3C Web Quality Assurance}},  
2002.

\bibitem{w3c04}
World Wide Web Consortium,
\emph{\href{http://www.w3.org/2004/04/webapps-cdf-ws/}{The W3C Workshop on Web Applications and Compound Documents}},  
2004.

\bibitem{pilgrim09}
Mark Pilgrim,
\emph{\href{http://diveintohtml5.info/index.html}{Dive Into HTML5}},  
2009-2011.

\bibitem{w3cvalidation}
World Wide Web Consortium,
\emph{\href{https://validator.w3.org/}{W3C Markup Validation Service}},  
1994-2012

\bibitem{nodesummit12}
Ryan Dahl,
\emph{\href{https://youtu.be/Fc26auhSLqM?t=1m32s}{Ryan Dahl Interview at Node Summit 2012}},  
2012

\bibitem{mongodb11}
MongoDB inc.,
\emph{\href{http://docs.mongodb.org/ecosystem/drivers/}{MongoDB Drivers}},  
2011-2015

\bibitem{google10}
Google,
\emph{\href{https://docs.angularjs.org/api?PHPSESSID=cae8e98e7ca559b4605d75c813b358ee}{Angular JS API Docs}},  
2010-2015

\bibitem{coppelia15}
Coppelia Robotics,
\emph{\href{http://www.coppeliarobotics.com/helpFiles/en/writingCode.htm}{Writing code in and around V-REP}},  
2015

\bibitem{creately12}
Creately,
\emph{\href{http://creately.com/blog/diagrams/uml-diagram-types-examples/}{The Complete Guide to UML Diagram Types with Examples}},  
2012

\bibitem{ambler01}
Scott W. Ambler,
\emph{\href{http://agilemodeling.com/}{Agile Modeling (AM) Effective Practices for Modeling and Documentation}},  
2001-2014

\bibitem{w3cgamepad15}
World Wide Web Consortium,
\emph{\href{http://www.w3.org/TR/gamepad/}{W3C Gamepad API Working Draft}},  
29 April 2015

\bibitem{caniusegamepad15}
caniuse.com,
\emph{\href{http://caniuse.com/\#feat=gamepad}{Browser Support Tables for Gamepad API.} Note: Table inaccurate with regards to mobile browsers: Chromium and Firefox mobile versions have support.},  
2015

\bibitem{caniusespeech15}
caniuse.com,
\emph{\href{http://caniuse.com/\#feat=speech-recognition}{Browser Support Tables for Speech Recognition API}},  
2015

\bibitem{nodejs15}
Node.js Foundation,
\emph{\href{https://nodejs.org/}{Node.js}},  
2015

\bibitem{angularjs15}
Google,
\emph{\href{https://angularjs.org/}{AngularJS Framework}},  
2010-2015

\bibitem{express15}
StrongLoop Inc,
\emph{\href{http://expressjs.com/}{Express Node Web Framework}},  
2015

\bibitem{mongodb15}
MongoDB Inc,
\emph{\href{https://www.mongodb.org/}{mongoDB}},  
2015

\bibitem{socketio15}
Socket.IO,
\emph{\href{http://socket.io/}{Socket.IO}},  
2015

\bibitem{ws11}
Einar Otto Stangvik,
\emph{\href{https://github.com/websockets/ws}{ws}},  
2011

\bibitem{nodepngjs12}
Kuba Niegowski,
\emph{\href{https://github.com/niegowski/node-pngjs}{node-pngjs}},  
2012

\bibitem{busboy13}
Brian White,
\emph{\href{https://github.com/mscdex/busboy}{busboy}},  
2013

\bibitem{monk12}
Guillermo Rauch,
\emph{\href{https://github.com/Automattic/monk}{monk}},  
2012

\bibitem{debug14}
TJ Holowaychuk,
\emph{\href{https://github.com/visionmedia/debug}{debug}},  
2014

\bibitem{annyang15}
Tal Ater,
\emph{\href{https://github.com/TalAter/annyang}{Annyang!}},  
2015

\bibitem{recordrtc15}
Muaz Khan,
\emph{\href{https://github.com/muaz-khan/WebRTC-Experiment/tree/master/RecordRTC}{RecordRTC}},  
2015

\bibitem{jsmpeg15}
Dominic Szablewski,
\emph{\href{https://github.com/phoboslab/jsmpeg}{jsmpeg}},  
2015

\bibitem{aurora15}
Audiocogs,
\emph{\href{https://github.com/audiocogs/aurora.js/}{aurora.js}},  
2015

\bibitem{auroraws15}
Fabien Brooke,
\emph{\href{https://github.com/fsbdev/aurora-websocket}{aurora.js websockets}},  
2015

\bibitem{googlemaps15}
Google,
\emph{\href{https://developers.google.com/maps/?hl=en}{Google Maps API}},  
2015

\bibitem{coppelia06}
Coppelia Robotics GmbH.,
\emph{\href{http://www.coppeliarobotics.com/helpFiles/en/remoteApiFunctionsPython.htm}{V-REP Python Remote API}},  
2006-2014 

\bibitem{kteam10}
K-Team,
\emph{\href{http://ftp.k-team.com/korebot/libkorebot-doc/main.html}{Khepera III KoreBot Library}},  
2010

\bibitem{bitcraze15}
Bitcraze,
\emph{\href{https://github.com/bitcraze/crazyflie-clients-python}{Crazyflie 2 Python Library}},  
2015

\bibitem{rollingspider15}
Jack Watson-Hamblin \& Chris Taylor,
\emph{\href{https://github.com/voodootikigod/node-rolling-spider}{Parrot Rolling Spider JavaScript Library} Note: use undocumented for time constraints and similarity with other integrations},  
2015

\bibitem{avconv15}
Libav.org,
\emph{\href{https://libav.org/}{avconv}},  
2015

\end{thebibliography}